Fourmile

### 2022-09-06 fourmile_dataprocess.Rmd
few updates

library(rmdformats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
library(rgdal)
library(sp)
library(sf)
library(mapview)
library(kableExtra)
library(dataRetrieval)
library(raster)
library(sf)

@@

```{r precip, echo=F}
#daily precip
prec_update <- prec %>%
  mutate(date = dmy(date),
         doy = yday(date)) %>%
  mutate(Gordon_South = ifelse(!doy %in% c(152:258), 
                               NA, Gordon_South),
         Gordon_North = ifelse(!doy %in% c(152:258), 
                               NA, Gordon_North),
         GH = ifelse(!doy %in% c(152:258), 
                               NA, GH),
         LM = ifelse(!doy %in% c(152:258), 
                               NA, LM),
         SE = ifelse(!doy %in% c(152:258), 
                               NA, SE),
         SP = ifelse(!doy %in% c(152:258), 
                               NA, SP),
         ST = ifelse(!doy %in% c(152:258), 
                               NA, ST),
         NADP_SL = ifelse(!doy %in% c(152:258), 
                               NA, NADP_SL)) %>%
  mutate_at(c('prism_W', 'prism_M', 'prism_E'), funs(lead), n = 1) #%>%
  mutate_at(c('prism_W', 'prism_M', 'prism_E'), )

daily_p <- prec %>%
  replace(.==-9999, NA) %>%
  pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
  mutate(precip_mm = as.numeric(precip_mm)) %>%
  mutate(WY = calcWaterYear(date))
  group_by(WY, site) %>%
  mutate(dailyp_cum_mm = cumsum(precip_mm))

@@

```{r}
niwot_prism <- read_csv(here('data', 'niwot_prism_compare.csv'))

ni_prism <- niwot_prism %>%
  filter(!row_number() %in% c(1:10)) %>%
  rename(date = 1,
         prism_mm = 2) %>%
  mutate(date = ymd(date))

niwot_snotel <- prec_update %>%
  dplyr::select(c(date, Niwot_Snotel)) %>%
  rename(snotel_mm = Niwot_Snotel)

niwot_compare <- full_join(ni_prism, niwot_snotel, by = 'date')

>>>>

library(rmdformats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
library(rgdal)
library(sp)
library(sf)
library(mapview)
library(kableExtra)
library(dataRetrieval)
library(raster)
library(sf)
library(stringr)

@@

```{r precip, echo=F}
#daily precip
prec_update <- prec %>%
  mutate(date = dmy(date),
         doy = yday(date)) %>%
  mutate_at(c('Gordon_South', 'Gordon_North',
              'GH', 'LM', 'SE', 'SP', 'ST', 'NADP_SL'),
            ~(ifelse(!doy %in% c(152:258), 
                               NA, .))) %>%
  mutate_at(c('prism_W', 'prism_M', 'prism_E'), list(lead), n = 1) %>%
  mutate_at(c('prism_W', 'prism_M', 'prism_E'), ~(ifelse(doy %in% c(152:258),
                                                         NA, .))) %>%
  filter(date > '2009-12-31') %>%
  dplyr::select(-c(doy)) %>%
  mutate(date = format(as.Date(date), '%d.%m.%Y'))

#write_csv(prec_update, 'precipAll_update.csv')

daily_p <- prec %>%
  mutate(date = dmy(date)) %>%
  replace(.==-9999, NA) %>%
  pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
  mutate(precip_mm = as.numeric(precip_mm)) %>%
  mutate(WY = calcWaterYear(date)) %>%
  group_by(WY, site) %>%
  mutate(dailyp_cum_mm = cumsum(precip_mm))

@@

```{r}
niwot_prism <- read.csv(here('data', 'niwot_prism_compare.csv')) %>% 
  filter(!row_number() %in% c(1:10)) %>%
   rename(date = 1,
          prism_mm = 2) %>%
   mutate(date = ymd(date),
          prism_mm = as.numeric(prism_mm))

niwot_snotel <- prec_update %>%
  dplyr::select(c(date, Niwot_Snotel)) %>%
  rename(snotel_mm = Niwot_Snotel) %>%
  mutate(date = dmy(date))

niwot_compare <- full_join(niwot_prism, niwot_snotel, by = 'date')
